Security Audit of Safeplug ``Tor in a Box''

### 2014-02-25 w2sp/report.tex
more edits

\begin{abstract}
%\boldmath
We present the first public third-party security audit of Pogoplug's Safeplug device, which marketed ``complete security and anonymity online'' by using Tor technology to protect users' IP addresses.  We examine the hardware, software, and network behavior of the Safeplug device, as well as the user experience in comparison to other forms of web browsing.  Although the Safeplug appears to use Tor as advertised, users may still be identified in ways they may not expect.  Furthermore, an engineering vulnerability in the Safeplug's settings commands would allow an adversary internal or external to user's home network to silently disable Tor or modify other Safeplug settings, which completely overrules the security claims of the device.  Even if the engineering problem is fixed, the user experience challenges of this type of device make it inferior to the existing standard in anonymity methods, the Tor Browser Bundle.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

Privacy on the Internet is becoming increasingly important as more users realize how vulnerable they are to being surveilled and attacked; anonymity has become the goal for many Internet users in order to protect themselves.  A recent study has shown that people have been the victim of many security-related issues, such as compromised emails/accounts, harrassment, stolen Social Security Number, bank information, and credit card numbers, due to their online visibility~\cite{pew}.  As the Internet grows and the amount of user information that is collected and/or provided online increases, users will continue to be more vulnerable.  According to this study, 86\% of internet users have tried to become more anonymous online by either clearing cookies, encrypting their email, or using virtual networks that mask their IP address~\cite{pew}.  While this study shows that a large percentage of users are taking measures to reduce their visibility online, 59\% reported that they don't believe it is possible to become completely anonymous online~\cite{pew}.

@@

\begin{itemize}
\item The Safeplug functions as a HTTP proxy inside the browser, which then uses Tor on outgoing traffic (see Figure \ref{fig:flow}).
\item The presence of both first- and third-party tracking cookies, de-anonymizing users across websites despite the presence of Tor.
\item A Cross-Site Request Forgery (CSRF) vulnerability that allows an outside attacker to modify the Safeplug settings (i.e., turning Tor on/off, turning ad-blocking on/off, turning the Tor relay on/off, adding/removing whitelisted sites from Tor).
\item A vulnerability that allows an attacker within the network to modify the Safeplug settings without notifying any other devices on the network of the change.
\item A higher latency than that of the Tor Browser Bundle.
\end{itemize}

@@

\section{Background}
{\bf Tor.} The state-of-the-art in online anonymity technology is the open-source project Tor.  Tor is a service that provides anonymous communication as an onion router; by encrypting internet traffic and sending it through layers of relays, a user can make it much more difficult to trace their internet use~\cite{tor}.  Instead of appearing to come from a user's IP address, the traffic will reach the destination from one of the relays, that will have received the traffic from another relay, creating a chain back from when the user first sent their traffic to a relay.  Tor is known as an onion router because each relay peels back one layer of encryption and no more, allowing it to send the traffic to the next destination but not allowing it to discover the origin or final recipient of the traffic.  Tor is open-source software developed by the Tor Project~\cite{torproject}.  Users of Tor are highly recommended to use it as part of the {\bf Tor Browser Bundle (TBB)}, which provides a single installation of a browser and the Tor software package.  This browser has special settings to prevent deanonymization of the traffic by other means, such as cookies, supercookies, or scripts~\cite{torproject}.

@@

{\bf Pogoplug.} Pogoplug, a subsidary of Cloud Engines, also offers a box for home network file sharing without needing to use a third-party storage provider.  Based on our examination of the box discussed below, we suspect that the Pogoplug box was relabelled as Safeplug and just uses different software to achieve its newly branded purpose.

\section{Design and Operation of Safeplug}
\subsection{Hardware}
Before investigating the software, we took apart one of the two Safeplug devices we purchased in order to see the physical components.  Figure~\ref{fig:top} shows the top of the board and Figure~\ref{fig:bottom} shows the bottom.  The board incorporates: (A) an SD card slot, (B) a power connector, (C) a USB slot, (D) an ethernet connector, (E) ethernet transceiver, (F) lan transformer, (G) the Marvell 88F6192 integrated controller, and (H), (I) flash memory.  The Marvell controller is from 2008 and runs ARM~\cite{marvellhw}. This is the same controller as version 4 of Pogoplug's cloud storage device - and takedowns of that device available online show an identical-looking circuit-board to the one in Figure~\ref{fig:circuit}\cite{pogo4}.  Also of note: the Safeplug branding is a sticker on the front of the device, whereas the Pogoplug branding is etched into the plastic on top of the device, which indicates that the Safeplug uses the same hardware as Pogoplug's existing devices, and derives its differing functionality from different software.

@@

If the majority of users can only understand the simpler description, then they likely won't understand the description of a Tor relay node.  This could be a problem if users simply decide not to do anything with that setting (i.e. don't change the setting to use Safeplug as a relay node).  Then there would be a large increase in use of the Tor network, yet most of the users are not giving back to it.

@@

@@

The Safeplug runs version 2.6.31.8 of Arch Linux on an ARM architecture, which was produced at the end of 2009 and installed on 23 August 2011.  Unsurprising for its age, there are a number of network vulnerabilities for this version of the kernel - most of which seem to produce denial of service attacks if an adversary sends a particularly formed packet \cite{kernelcve}.  This is the same version of Linux that runs on Version 4 of PogoPlug's Mobile platform \cite{archforum}.

The software installed by the activation process on the Safeplug (it is not on the box prior to the activation) is in \verb!/opt/xce! and includes lighttpd, privoxy, and tor.  Lighttpd is an open-source webserver, which is serving the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [... while being] designed and optimized for high perfomance environments'' \cite{lighttpd}.  The version of lighttpd on the box is only one version away from being up to date, 1.4.33 which was released on 27 September 2013.  The current version of lighttpd, which has a number of security fixes, was released on 20 January 2014, after the Safeplug was purchased.  However, checking for an update from the Safeplug does not lead to any updated software installation, one of many cases of inattention to detail.

@@

\subsection{Networking}
The lighttpd, Privoxy and Dropbear software give some indication of the networking services on the device.  We used \texttt{nmap} to scan the ports.  Before the activation of the Safeplug, only ports 80 and port 3333 are open.  After the activation, without the use of Tor turned on, ports 22 for SSH, port 80 for settings access and port 8080 for http-proxy are open.  When Tor is turned on as a relay, port 9001 tor-orport is opened as well.  This corresponds with the note on the settings page about Tor relays discussed in Section \ref{port9001} above.

@@

\section{Usability}
Several aspects of the user experience of the Safeplug affect the usability and security of the device.  The Safeplug advertisements highlighted the ease of setup and activation of the device

@@

Next, we wanted to see how usable this would be to a normal Internet user.  A user would probably decide not to use Safeplug if they could not read their web pages (if they were not in their native language), or if they could not log into their accounts (some web sites will lock a user out if they try to log in from multiple countries in a short time period).  While browsing the Internet, we experienced some pages in German and Swedish, which is expected with Tor; if a user is not familiar with Tor, then they may just get frustrated and stop using Safeplug altogether.  We were also prompted with a request to ``Enter the name of the city where you usually sign in'' when we tried to log into our Google account, indicating that Google noticed we were trying to login from significantly ``unusual'' location.

\subsection{Cookies}  
While browsing the Internet, we logged into a Google Account in a tab, and then subsequently went to a website that had the Google+ logo in a different tab.  When we clicked on the Google+ logo, it remember who we are; so we can confirm that we still have first-party cookies.  We experienced the same situation with Facebook and its corresponding ``like'' button.

@@

More interesting and damaging to the user's control over their anonymity would be third-party cookies because the user cannot remove those just by logging out.  It requires a trip to the browser settings to clear cookies (or not have them set in the first place).  We used the FourthParty plugin developed by Jonathan Mayer at Stanford to collect information about cookies and other browsing data during the client's use of the Safeplug \cite{fourthparty}.  When collecting data on the existence of third-party cookies, we analyzed two separate browsing sessions; they were both new sessions with no cookies.  One of the sessions used the ad-block feature of the Safeplug and the other did not.  After analyzing data from Fourthparty, we found many third-party cookies in both sessions.  These included cookies from: abmr.net, bizographics.com, krxd.net, and bluekai.com among many others.

@@

\subsection{Insider Attack}
Since the RPC server does not perform any kind of validation or authentication on the settings strings, it would be easy for anyone inside the local network to send a command and change the settings, for example to disable Tor or adblocking.  All the attacker would need to know is the IP of the device.  It does not even require SSH or discovering the (publically available) root password, or the user's new root password if they have been well-informed and adept enough to change it.  Figure \ref{disable} shows an example of this attack.

This attacker could also be any kind of device on the local network, or the local gateway if it is compromised.  The NSA ``Spymall'' catalog leaked in December shows tools for compromising a number of different devices and home routers are traditionally insecure \cite{spymall}.  It is easy to imagine any malicious party, not just one with the resources of a government, (although governments might be some of the most interested parties in attacking a Tor proxy) compromising the gateway and using that access to make a disabling RPC call into the Safeplug.  This would occur silently from the perspective of a client unless they happen to check the Settings page for the Safeplug.  Instead, the client would continue browsing with a belief that they are protected by their use of the Tor network, while in fact any external adversary can track their traffic.

@@

The largest observed time to send requests to the 192.168.0.0/24 space was approximately 400 milliseconds; the entire attack costs approximately 800 milliseconds for sending request to both 192.168.0.0/24 and 192.168.1.0/24 ranges - even when the website was being loaded over Tor.  In the case of a private network in the range of 172.16.0.0/16, the attack took less than ~12 minutes (this generates script timeout warnings in most major browsers, which affects the timing of this attack).  This means that it would take a few hours to send requests to the full 172.16.0.0/12 range, which is commonly used in business networks.  The final private network space is 10.0.0.0/8 which is too large for an exhaustive search, but some simple optimization might make it feasible as well.  For example, using a GET request to get and parse the Safeplug settings page would allow the script to positively identify the safeplug and stop the search.  However, the 192.168.0.0/24 and 192.168.1.0/24 ranges are much more common in home networks; because Safeplug is geared towards home network use, in most cases the script will take less than a second, a trivial amount of time for the attacker to spend.

@@

Obviously having a publically available root password means that SSH can be done effectively without authentication.  We tried the SSH procedure twice, once before the internet connection and activation, and once afterwards.  Before the activation and update procedure, SSH was not available.  The simple \verb!Hbplug! software on the box could not accept this RPC call.  However, once the box was updated and had lighttpd installed, the SSH procedure was available and we could download the contents of the root filesystem for analysis.

\subsection{Spoofing the Update Server}
\label{dnsspoof}
A more dangerous class of vulnerabilities comes from the fact that the update process happens over insecure TCP rather than any kind of encrypted process.  During our network analysis of the activation process, we discovered that the update script is downloaded via TCP from an IP address provided by the pogoplug servers.  This update script (run as root) then downloads the Safeplug's software (Tor, Privoxy, Lighttpd, and wget) and checks it against MD5 hashes, but it is not clear whether there is suitable verification of the update script itself.  An adversary could use DNS spoofing or compromise the Pogoplug server in order to force users to download a malicious update script - for example, something that turns the Safeplug into a surveillance box while appearing to provide the correct functionality.  Since the most efficient way to check this would be to verify the contents of the Safeplug box itself by SSHing in, and SSHing explicitly breaks the warranty, it is clear that any kind of mitigation to this attack would be beyond an average user.  Because the activation occurs over TCP rather than anything more secure, an adversary who can spoof DNS replies to the user has a paved gateway into the Safeplug box.  This turns a device that does not live up to expectations but is otherwise harmless into something that actively harms security on the network.

@@

{\bf Fingerprinting.}  Website fingerprinting attacks as well as remote physical device fingerprinting attacks have shown they can identify users, even when specific defenses have been used in order to prevent these attacks. Previous research has shown that web page fingerprinting attacks are possible~\cite{dyer, herrmann, panchenko}.  Cai, Zhang, Joshi, and Johnson introduced both a web page and website fingerprinting attack that defeats many recently proposed defenses, including cover traffic and randomized pipeling.  They find that their attack is successful 83.7\% of the time when the defense is the use of Tor; the success rate decreases to 52.2\% when the defense is the use of Tor, randomized pipelining, padding packets to 1500 bytes, and adding cover traffic at a 1:1 ratio~\cite{fingerprint1}.  These results can be extended to the security of Safeplug.  Because Safeplug uses only Tor to anonymize users, it may be susceptible to this type of fingerprinting attack.

@@

\section{Discussion}
\subsection{Engineering Fixes}
The most critical engineering fix is authentication in the POST calls to prevent the cross-site request forgery attack.  A typical example is a cookie and a hidden form field set in the Settings page the Safeplug hosts; the cookie must be returned by the browser when making the POST request to the RPC server \cite{csrfdef}.  Although someone doing a cross-site request forgery attack such as the one described above could get the cookie sent, because of the same-origin policy, the adversary would not be able to examine the contents of the cookie to determine what to put in the form field.

@@

One type of client that deserves special attention is a non-Android mobile phone user.  Although the Tor Project publishes an Android app called Orbot on the Android Market \cite{orbot} which is supported for Android versions 2.3 and later \cite{amorbot}, there are no official Tor apps for iPhones or other non-Android devices.  Safeplug provides proxy functionality and instructions for Safari on the iPhone; however, this would only work while the user is on that wifi network that the Safeplug routes through.  If any data is sent over the cellular network or another wifi network, then the security of Tor is lost.  Additionally, the user may have to disable the proxy whenever they move to a different network, and remember to re-enable it when they want to use Tor.  This is certainly not transparent usability.  Users who are truly concerned about anonymity online should eschew the Safeplug and purchase a device that supports the Tor Browser Bundle or other Tor Project software.

\subsection{Opportunities}
Despite all the structural problems, is there a market for a Torifying piece of hardware?  Given the security pitfalls in comparison to a piece of software such as the Tor browser bundle, there seems to be no reason for a user that can run the Tor browser bundle to purchase the Safeplug or any other device.  For mobile phones, the proxy problems with mobility contribute to an already high usability cost.  However, there are an emerging class of ``smart home'' devices which may connect to the internet.  It is possible that some of these devices can be configured to use an HTTP proxy or some other middle box to Torify their traffic to an external service provider.  For them, is the benefit of some anonymity via a Safeplug-like device worthwhile?  Since the data sent by these devices to the service provider likely contains lots of identifying information, the use of Tor probably only protects the user's location at the expense of connection time and load on the Tor network.  Since proxy configuration on such devices is likely to be difficult and the amount of information hidden is unlikely to be worth the effort, a Torifying box that functions as a proxy has questionable use in this space as well.

\section{Conclusion}
Ultimately, the structural concerns of the Safeplug ``Torifying proxy-in-a-box'' strategy indicate that this is not the correct method for security and anonymity online.  It is critical for Safeplug to correct their engineering errors, particularly the vulnerability to silent disabling of Tor in order to protect customers who have already made use of the device, but users who are truly concerned about safety and anonymity online should make use of technologies directly from the Tor Project.

>>>>

\begin{abstract}
%\boldmath
We present the first public third-party security audit of Pogoplug's Safeplug device, which marketed ``complete security and anonymity online'' by using Tor technology to protect users' IP addresses.  We examine the hardware, software, and network behavior of the Safeplug device, as well as the user experience in comparison to other forms of web browsing.  Although the Safeplug appears to use Tor as advertised, users may still be identified in ways they may not expect.  Furthermore, an engineering vulnerability in the Safeplug's settings commands would allow an adversary internal or external to a user's home network to silently disable Tor or modify other Safeplug settings, which completely overrules the security claims of the device.  Even if the engineering problem is fixed, the user experience challenges of this type of device make it inferior to the existing standard in anonymity methods, the Tor Browser Bundle.
\end{abstract}
% IEEEtran.cls defaults to using nonbold math in the Abstract.
% This preserves the distinction between vectors and scalars. However,
% if the conference you are submitting to favors bold math in the abstract,
% then you can use LaTeX's standard command \boldmath at the very start
% of the abstract to achieve this. Many IEEE journals/conferences frown on
% math in the abstract anyway.

@@

Privacy on the Internet is becoming increasingly important as more users realize how vulnerable they are to surveillance and attacks; anonymity has become the goal for many Internet users in order to protect themselves.  A recent study has shown that people have been the victim of many security-related issues, such as compromised emails/accounts, harrassment, stolen Social Security Numbers, bank information, and credit card numbers, due to their online visibility~\cite{pew}.  As the Internet grows and the amount of user information that is collected and/or provided online increases, users will continue to be more vulnerable.  According to this study, 86\% of internet users have tried to become more anonymous online by either clearing cookies, encrypting their email, or using virtual networks that mask their IP address~\cite{pew}.  While this study shows that a large percentage of users are taking measures to reduce their visibility online, 59\% reported that they don't believe it is possible to become completely anonymous online~\cite{pew}.

@@

\begin{itemize}
\item The Safeplug functions as a HTTP proxy inside the browser, which then uses Tor on outgoing traffic (see Figure \ref{fig:flow}).
\item The presence of both first- and third-party tracking cookies, de-anonymizing users across websites despite the presence of Tor.
\item A Cross-Site Request Forgery (CSRF) vulnerability that allows an outside attacker to modify the Safeplug settings (i.e., turning Tor on/off, turning ad-blocking on/off, turning the Tor relay setting on/off, adding/removing whitelisted sites from Tor).
\item A vulnerability that allows an attacker within the network to modify the Safeplug settings without notifying any other devices on the network.
\item A higher latency than that of the Tor Browser Bundle.
\end{itemize}

@@

\section{Background}
{\bf Tor.} The state-of-the-art in online anonymity technology is the open-source project Tor.  Tor is a service that provides anonymous communication as an onion router; by encrypting internet traffic and sending it through layers of relays, a user can make it much more difficult to trace their internet use~\cite{tor}.  Instead of appearing to come from a user's IP address, the traffic will reach the destination from one of the relays, that will have received the traffic from another relay, creating a chain back from when the user first sent their traffic to a relay.  Tor is known as an onion router because each relay peels back one layer of encryption and no more, allowing it to send the traffic to the next destination but not allowing it to discover the origin or final recipient of the traffic.  Tor is open-source software developed by the Tor Project~\cite{torproject}.  Users of Tor are highly recommended to use it as part of the Tor Browser Bundle, which provides a single installation of a browser and the Tor software package.  This browser has special settings to prevent deanonymization of the traffic by other means, such as cookies, supercookies, or scripts~\cite{torproject}.

@@

{\bf Pogoplug.} Pogoplug, a subsidary of Cloud Engines, also offers a box for home network file sharing without needing to use a third-party storage provider.  Based on our examination of the box discussed below, we suspect that the Pogoplug box was relabelled as Safeplug and simply uses different software to achieve its newly branded purpose.

\section{Design and Operation of Safeplug}

@@

If the majority of users can only understand the simpler description, then they likely won't understand the description of a Tor relay node.  This could be a problem if users simply decide not to do anything with that setting (i.e. don't change the setting to use Safeplug as a relay node).  In this case, there would be a large increase in use of the Tor network, yet most of the users are not giving back to it.

@@

\subsection{Hardware}
Before investigating the software, we took apart one of the two Safeplug devices we purchased in order to see the physical components.  Figure~\ref{fig:top} shows the top of the board and Figure~\ref{fig:bottom} shows the bottom.  The board incorporates: (A) an SD card slot, (B) a power connector, (C) a USB slot, (D) an ethernet connector, (E) ethernet transceiver, (F) lan transformer, (G) the Marvell 88F6192 integrated controller, and (H), (I) flash memory.  The Marvell controller is from 2008 and runs ARM~\cite{marvellhw}. This is the same controller as version 4 of Pogoplug's cloud storage device - and takedowns of that device available online show an identical-looking circuit-board to the one in Figure~\ref{fig:circuit}\cite{pogo4}.  Also of note: the Safeplug branding is a sticker on the front of the device, whereas the Pogoplug branding is etched into the plastic on top of the device, which indicates that the Safeplug uses the same hardware as Pogoplug's existing devices, and derives its differing functionality from different software.

@@

The Safeplug runs version 2.6.31.8 of Arch Linux on an ARM architecture, which was produced at the end of 2009 and installed on 23 August 2011.  Unsurprising for its age, there are a number of network vulnerabilities for this version of the kernel - most of which produce denial of service attacks if an adversary sends a particularly formed packet \cite{kernelcve}.  This is the same version of Linux that runs on Version 4 of PogoPlug's Mobile platform \cite{archforum}.

The software installed by the activation process on the Safeplug is in \verb!/opt/xce! and includes lighttpd, privoxy, and tor.  Lighttpd is an open-source webserver, which is serving the settings page on the device - the project's description mentions ``security, speed, compliance, and flexibility [... while being] designed and optimized for high perfomance environments'' \cite{lighttpd}.  The version of lighttpd on the box is only one version away from being up to date, 1.4.33 which was released on 27 September 2013.  The current version of lighttpd, which has a number of security fixes, was released on 20 January 2014, after the Safeplug was purchased.  However, checking for an update from the Safeplug does not lead to any updated software installation.

@@

\subsection{Networking}
The lighttpd, Privoxy, and Dropbear software give some indication of the networking services on the device.  We used \texttt{nmap} to scan the ports.  Before the activation of the Safeplug, only ports 80 and port 3333 are open.  After the activation, without the use of Tor turned on, ports 22 for SSH, port 80 for settings access and port 8080 for http-proxy are open.  When Tor is turned on as a relay, port 9001 tor-orport is opened as well.  This corresponds with the note on the settings page about Tor relays discussed in Section \ref{port9001} above.

@@

\section{Usability}
Several aspects of the user experience of the Safeplug affect the usability and security of the device.  The Safeplug advertisements highlighted the ease of setup and activation of the device.

@@

Next, we wanted to see how usable this would be to a normal Internet user.  A user would probably decide not to use Safeplug if they could not read their web pages (if they were not in their native language), or if they could not log into their accounts (some web sites will lock a user out if they try to log in from multiple countries in a short time period).  While browsing the Internet, we experienced some pages in German and Swedish, which is expected with Tor; if a user is not familiar with Tor, they may just get frustrated and stop using Safeplug altogether.  We were also prompted with a request to ``Enter the name of the city where you usually sign in'' when we tried to log into our Google account, indicating that Google noticed we were trying to login from significantly ``unusual'' location.

\subsection{Cookies}  
While browsing the Internet, we logged into a Google Account in a tab, and then subsequently went to a website that had the Google+ widget in a different tab.  When we clicked on the Google+ widget, it remember who we are; so we can confirm that we still have first-party cookies.  We experienced the same situation with Facebook and its corresponding ``like'' button.  This was confirmed by using FourthParty, a plugin developed by Jonathan Mayer at Stanford to collect information about cookies and other browsing data.

@@

More interesting and damaging to the user's control over their anonymity would be third-party cookies because the user cannot remove those just by logging out.  It requires a trip to the browser settings to clear cookies (or not have them set in the first place).  We used FourthParty to analyze the client's use of the Safeplug \cite{fourthparty}.  When collecting data on the existence of third-party cookies, we analyzed two separate browsing sessions; they were both new sessions with no cookies.  One of the sessions used the ad-block feature of the Safeplug and the other did not.  After analyzing data from Fourthparty, we found many third-party cookies in both sessions.  These included cookies from: abmr.net, bizographics.com, krxd.net, and bluekai.com among many others.

@@

\subsection{Insider Attack}
Since the RPC server does not perform any kind of validation or authentication on the settings strings, it would be easy for anyone inside the local network to send a command and change the settings, for example to disable Tor or adblocking.  All the attacker would need to know is the IP address of the device.  It does not require SSH or discovering the (publically available) root password, or the user's new root password if they have been well-informed and adept enough to change it.  Figure \ref{disable} shows an example of this attack.

This attacker could also be any kind of device on the local network, or the local gateway if it is compromised.  The NSA ``Spymall'' catalog leaked in December shows tools for compromising a number of different devices and home routers are traditionally insecure \cite{spymall}.  It is easy to imagine any malicious party, not just one with the resources of a government (although governments might be some of the most interested parties in attacking a Tor proxy), compromising the gateway and using that access to make a disabling RPC call into the Safeplug.  This would occur silently from the perspective of a client unless they happen to check the Settings page for the Safeplug.  Instead, the client would continue browsing with a belief that they are protected by their use of the Tor network, while in fact any external adversary can track their traffic.

@@

The largest observed time to send requests to the 192.168.0.0/24 space was approximately 400 milliseconds; the entire attack costs approximately 800 milliseconds for sending requests to both 192.168.0.0/24 and 192.168.1.0/24 ranges - even when the website was being loaded over Tor.  In the case of a private network in the range of 172.16.0.0/16, the attack took less than ~12 minutes (this generates script timeout warnings in most major browsers, which affects the timing of this attack).  This means that it would take a few hours to send requests to the full 172.16.0.0/12 range, which is commonly used in business networks.  The final private network space is 10.0.0.0/8 which is too large for an exhaustive search, but some simple optimization might make it feasible as well.  For example, using a GET request to get and parse the Safeplug settings page would allow the script to positively identify the Safeplug and stop the search.  However, the 192.168.0.0/24 and 192.168.1.0/24 ranges are much more common in home networks; because Safeplug is geared towards home network use, in most cases the script will take less than a second, a trivial amount of time for the attacker to spend.

@@

Having a publically available root password means that SSH can be done effectively without authentication.  We tried the SSH procedure twice, once before the Internet connection and activation, and once afterwards.  Before the activation and update procedure, SSH was not available.  The simple \verb!Hbplug! software on the box could not accept this RPC call.  However, once the box was updated and had lighttpd installed, the SSH procedure was available and we could download the contents of the root filesystem for analysis.

\subsection{Spoofing the Update Server}
\label{dnsspoof}
A more dangerous class of vulnerabilities comes from the fact that the update process happens over insecure TCP rather than any kind of encrypted process.  During our network analysis of the activation process, we discovered that the update script is downloaded via TCP from an IP address provided by the Pogoplug servers.  This update script (run as root) then downloads the Safeplug's software (Tor, Privoxy, Lighttpd, and wget) and checks it against MD5 hashes, but it is not clear whether there is suitable verification of the update script itself.  An adversary could use DNS spoofing or compromise the Pogoplug server in order to force users to download a malicious update script - for example, something that turns the Safeplug into a surveillance box while appearing to provide the correct functionality.  Since the most efficient way to check this would be to verify the contents of the Safeplug box itself by SSHing in, it is clear that any kind of mitigation to this attack would be beyond an average user.  Because the activation occurs over TCP rather than anything more secure, an adversary who can spoof DNS replies to the user has a paved gateway into the Safeplug box.  This turns a device that does not live up to expectations, but is otherwise harmless, into something that actively harms security on the network.

@@

{\bf Fingerprinting.}  Website fingerprinting attacks as well as remote physical device fingerprinting attacks have shown they can identify users, even when specific defenses have been used in order to prevent them. Previous research has shown that web page fingerprinting attacks are possible~\cite{dyer, herrmann, panchenko}.  Cai, Zhang, Joshi, and Johnson introduced both a web page and website fingerprinting attack that defeats many recently proposed defenses, including cover traffic and randomized pipeling.  They find that their attack is successful 83.7\% of the time when the defense is the use of Tor; the success rate decreases to 52.2\% when the defense is the use of Tor, randomized pipelining, padding packets to 1500 bytes, and adding cover traffic at a 1:1 ratio~\cite{fingerprint1}.  These results can be extended to the security of Safeplug.  Because Safeplug uses only Tor to anonymize users, it may be susceptible to this type of fingerprinting attack.

@@

\section{Discussion}
\subsection{Engineering Fixes}
The most critical engineering fix is authentication in the POST calls to prevent the CSRF attack.  A typical example is a cookie and a hidden form field set in the Settings page of the Safeplug hosts; the cookie must be returned by the browser when making the POST request to the RPC server \cite{csrfdef}.  Although someone doing a CSRF attack such as the one described above could get the cookie sent, because of the same-origin policy, the adversary would not be able to examine the contents of the cookie to determine what to put in the form field.

@@

One type of client that deserves special attention is a non-Android mobile phone user.  Although the Tor Project publishes an Android app called Orbot on the Android Market, which is supported for Android versions 2.3 and later, there are no official Tor apps for iPhones or other non-Android devices~\cite{orbot,amorbot}.  Safeplug provides proxy functionality and instructions for Safari on the iPhone; however, this would only work while the user is on that wifi network that the Safeplug routes through.  If any data is sent over the cellular network or another wifi network, then the security of Tor is lost.  Additionally, the user may have to disable the proxy whenever they move to a different network, and remember to re-enable it when they want to use Tor.  This is certainly not transparent usability.  Users who are truly concerned about anonymity online should eschew the Safeplug and purchase a device that supports the Tor Browser Bundle or other Tor Project software.

\subsection{Opportunities}
Despite all the structural problems, is there a market for a Torifying piece of hardware?  Given the security pitfalls in comparison to a piece of software such as the Tor Browser Bundle, there seems to be no reason for a user that can run the Tor Browser Bundle to purchase the Safeplug or any other device.  For mobile phones, the proxy problems with mobility contribute to an already high usability cost.  However, there are an emerging class of ``smart home'' devices which may connect to the internet.  It is possible that some of these devices can be configured to use an HTTP proxy or some other middle box to Torify their traffic to an external service provider.  For them, is the benefit of some anonymity via a Safeplug-like device worthwhile?  Since the data sent by these devices to the service provider likely contains identifying information, the use of Tor probably only protects the user's location at the expense of connection time and load on the Tor network.  Since proxy configuration on such devices is likely to be difficult and the amount of information hidden is unlikely to be worth the effort, a Torifying box that functions as a proxy has questionable use in this space as well.

\section{Conclusion}
Ultimately, the structural concerns of the Safeplug ``Torifying proxy-in-a-box'' strategy indicate that this is not the correct method for security and anonymity online.  It is critical for Safeplug to correct their engineering errors, particularly the vulnerability to silently disable Tor, in order to protect customers who have already made use of the device, but users who are truly concerned about safety and anonymity online should make use of technologies directly from the Tor Project.
